---
title: "Lab 3"
author: "Rui Zong"
date: "11/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# 1.Download prices for the SPY ETF, dating between 2020-01-01 and 2022-09-30
# 2.Compute the daily log-returns over this sample period (no need to report)
# 3.Assume that the price follows a GBM. Calibrate the model and report both mu and sigma (hats)




```{r pressure, echo=FALSE}
library(quantmod)
library(lubridate)
rm(list = ls())
P <- get(getSymbols("SPY",from = "1900-01-01"))[,6]
P <- P["2020-01-01/2022-09-30",]
P_w <- apply.weekly(P,last)
R <- na.omit(log(P/lag(P)))
R_w <- na.omit(log(P_w/lag(P_w)))
dt <- 1/252
m <- mean(R)
s <- sd(R)
sig <- s/sqrt(dt)
mu <- m/dt + (sig^2)/2
data.frame(mu = mu, sig = sig)
```
# 4. After calibration, simulate the future price over a one-year period based on the closing price from  2022-09-30. Create at least 1000 simulations and provide a couple of plots as a summary. 
```{r}
N <- 10^5
dt <- 1/252
T_end <- 1 # one year from now
periods <- T_end/dt # number of days to simulate ahead
S0 <- as.numeric(P["2022-09-30",]) # last price of SPY
drift <- mu - (sig^2)/2
sim_Geo_BM <- function(n,drift,sig) {
  set.seed(n)
  R_seq <- rnorm(periods,drift*dt,sig*sqrt(dt)) # need to simulate returns 
  S <- S0*exp(c(0,cumsum(R_seq))) # take the exp of returns
  return(S)
}
S_mat <- sapply(1:N,function(x) sim_Geo_BM(x,drift,sig) )
data.frame(True = S0*exp(mu*T_end), Simulated = mean(S_mat[nrow(S_mat),]))
true_var <- (S0^2)*(exp(T_end*sig^2) - 1)*exp((2*T_end*mu))
sim_var <- var(S_mat[nrow(S_mat),])
data.frame(True_Variance = true_var, Sim_Variance = sim_var )
```
#5.What is the one-year VaR(0.05)?

```{r}
S_end <- S_mat[nrow(S_mat),]

S_t_bar <- mean(S_end)
Q_t_c <- quantile(S_end,0.05)
VaR_0.05_d <- S_t_bar - Q_t_c
VaR_0.05_d
```


```{r}
VaR_c_f <- function(x) S_t_bar - quantile(S_end,x)
c_seq <- seq(0.1,0.001,length = 20)
VaR_seq <- VaR_c_f(c_seq)
plot(VaR_seq~c_seq, pch = 20) 
lines(predict(loess(VaR_seq~c_seq),c_seq) ~ c_seq, lty = 2) 
grid(10)
```

#6.Repeat the above tasks using weekly returns and report the VaR(0.05).
```{r}
dt <- 1/52 # for weekly
periods <- T_end/dt # update number of periods m <- mean(R_w)
s <- sd(R_w)
sig_w <- s/sqrt(dt)
mu_w <- m/dt + (sig_w^2)/2
data.frame(mu = mu_w, sig = sig_w)

```


```{r}
cor(R,lag(R),use = "pairwise")
```


```{r}
cor(R_w,lag(R_w),use = "pairwise")
```
```{r}
#Note that expected value does nit change that much from daily since μ estimate did not change much:
N <- 10^5
drift_w <- mu_w - (sig_w^2)/2
S_mat <- sapply(1:N,function(x) sim_Geo_BM(x,drift_w,sig_w) )
data.frame(True = S0*exp(mu_w*T_end), Simulated = mean(S_mat[nrow(S_mat),]))
```


```{r}
true_var <- (S0^2)*(exp(T_end*sig_w^2) - 1)*exp((2*T_end*mu_w))
sim_var <- var(S_mat[nrow(S_mat),])
data.frame(True_Variance = true_var, Sim_Variance = sim_var )
```


```{r}
S_end <- S_mat[nrow(S_mat),]
S_t_bar <- mean(S_end)
Q_t_c <- quantile(S_end,0.05)
VaR_0.05 <- S_t_bar - Q_t_c
VaR_0.05
```

#7.How do the results from tasks 5 and 6 compare? Should it matter whether it is daily or weekly
```{r}

#
#Main Takeaway: the more we aggregate returns using the iid assumption, the more we are likely #to overstate/understate the true risk of the asset/portfolio. It is important to take into #consideration whether the iid assumption is strongly or weakly rejected. For this reason, we #observe different values when we weekly versus daily regardless of the computed metric of #interest.
#

```

#8.Finally, suppose that you work with the weekly data. Let us consider some sensitivity #analysis and address the following questions:
#1How much does the one-year VaR(0.05) increase if the annual volatility increases by 5%? 
#2Is the relationship between one-year VaR(0.05) and the annual volatility linear? 
```{r}
#Part1
N <- 10^3
VaR_sig_fun <- function(sig_value) {
  S_mat <- sapply(1:N,function(x) sim_Geo_BM(x,drift_w,sig_value) ) 
  S_end <-S_mat[nrow(S_mat),]
  S_t_bar <- mean(S_end)
  Q_t_c <- quantile(S_end,0.05)
  VaR_0.05 <- S_t_bar - Q_t_c
  return(VaR_0.05)
}
sig_seq <- seq(0.1,0.5,length = 20)
VaR_seq <- sapply(sig_seq,VaR_sig_fun)
plot(VaR_seq~sig_seq,type = "l")
```


```{r}
VaR_sig_fun(sig_w + 0.05)/VaR_sig_fun(sig_w) - 1

```

```{r}
#Part 2
VaR_sig_fun(sig_w + 0.1)/VaR_sig_fun(sig_w + 0.05) - 1
```


```{r}
VaR_sig_fun(sig_w + 0.2)/VaR_sig_fun(sig_w + 0.15) - 1
```


```{r}

VaR_sig_fun(sig_w + 0.4)/VaR_sig_fun(sig_w + 0.35) - 1

```


```{r}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
